Modelling latitudinal temperature gradients from geological proxies: An early Eocene example

### 2022-07-04 manuscript/manuscript.Rmd
thoughts on title and figures

---
title: "Article title goes here"
author: 
  - Kilian Eichenseer^[Department of Earth Sciences, Durham University, South Road, DH1 3LE, Durham, United Kingdom] and Lewis A. Jones^[Centro de Investigación Mariña, Grupo de Ecoloxía Animal, Universidade de Vigo, 36310 Vigo, Spain]
output: 
  word_document:
    reference_docx: "template.docx"
bibliography: references.bib
csl: palaeontology.csl
---

@@

>>>>

---
title: "Modelling latitudinal temperature gradients from geological proxies: An early Eocene example"
author: 
  - Kilian Eichenseer^[Department of Earth Sciences, Durham University, South Road, DH1 3LE, Durham, United Kingdom] and Lewis A. Jones^[Centro de Investigación Mariña, Grupo de Ecoloxía Animal, Universidade de Vigo, 36310 Vigo, Spain]
output: 
  word_document:
    reference_docx: "template.docx"
bibliography: references.bib
csl: palaeontology.csl
---

@@

## Fig 1 - Model structure and proof of concept with modern data
## Fig 2 - Eocene example
## Fig 3 - Showing influence of changing model assumptions
